Supervised Learning for Psychological Attention to High School Students

### 2020-11-15 article/article.tex
[ article ] finished introduction

The present work is oriented to the application of supervised learning
techniques (decision trees, support vector machines and neural networks) for
classifying the data from the survey, aiming for the construction of a model to
detect individuals with mental health issues. This document is organized as
follows: Section \ref{sec:start} gives a short review of the current literature
of supervised techniques in this application area, Section \ref{sec:meth} shows
the general methodology used in this work, moreover Section \ref{sec:res} shows
the obtained results over the data and slight modifications, finally Section
\ref{sec:conc} concludes this work and sets pillars for future works.

\section{State of the Art}\label{sec:start}

>>>>

The present work is oriented to the application of supervised learning
techniques (decision trees, support vector machines and neural networks) for
classifying the data from the survey, aiming for the construction of a model to
detect individuals with mental health issues. Recent developments and the
increasing popularity of supervised techniques has contributed to their
application in different areas, among them, mental health.

The novel work by \textcite{thieme2020} makes and excellent literature review of
Machine Learning (ML) in mental health, including the current state-of-the-art
and formulates new strategies for integrating human-oriented research with
multi-disciplinary. They also conclude that ML applied in mental health is
``still in its infancy'' given the complexity and difficulties of constructing
robust models for clinically reliable outputs.

Additionally, the work presented by \textcite{shatte2019} is also a complete
compendium of recent ML applications in mental health, including the usage
of Support Vector Machines (SVMs), Decision Trees (DTs), Neural Networks (NN)
and beyond. This paper includes a systematic review of over three hundred papers
and it concludes that these techniques have brought benefits 
across the areas of diagnosis, treatment, research and clinical administration.

Finally, another overview of applications of Artificial Intelligence (AI) for Mental 
Illnesses is the research published by \textcite{graham2019}, where the authors
reviewed 28 research papers which include modern methodologies (and 
technologies) for predicting or classifying psychological illnesses such as 
depression, schizophrenia or suicidal behavior. The study discusses how the
application of AI techniques supports the clinical practice while considering its
limitations, it also presents some ethical implications and states which areas need
further development.

This document is organized as
follows: Section \ref{sec:meth} shows the general methodology used in this work,
moreover Section \ref{sec:res} shows the obtained results over the data and
slight modifications, finally Section \ref{sec:conc} concludes this work and
sets pillars for future works.
